### 2016-04-15 manuscript.tex
More edits

\section{Weighted Linkage Disequilibrium} As \cite{loh2013inferring} noted, we
cannot use the LD in the admixed population directly, because the allele
frequency differences in the source populations can be of either sign. As in As
\cite{loh2013inferring} , we solve this problem by computing the product of the
values of the three-point linkage disequilibrium coefficient with the product of
the allele frequency differences. Using equation \ref{local_ancestry} we obtain $$
\delta_x\delta_y\delta_z
D_3(d,d')=\delta_x^2\delta_y^2\delta_z^2\mathbb{E}[\text{cov}(A_x,A_y,A_z)], $$
because the local ancestry in the admixed sample is independent of the allele
frequencies in the admixed population. For inference purposes, we estimate this
function by averaging over triples of SNPs which are separated by distances of
approximately $d$ and $d'$. The LD term is estimated from the admixed
population, while the $\delta$'s are estimated from reference populations which
are closely related to the two source populations. We notice that both this
approach, as well as the previous approaches (e.g., \cite{loh2013inferring} ),
does not take genetic drift in the source populations after the time of
admixture into account, i.e. there is an assumption of both this mehtod and
previous methods that the allele frequencies in the ancestral source populations
can be approximated well using the allele frequencies in the extant populations.

@@

The time complexities for the binning and the FFT's are $O(S_n)$ and
$O(P^2\log(P))$. Of these two, the first term will dominate, because the number
of bins much less than the number of segregating sites.

>>>>

\section{Weighted Linkage Disequilibrium} As \cite{loh2013inferring} noted, we
cannot use the LD in the admixed population directly, because the allele
frequency differences in the source populations can be of either sign. As in
\cite{loh2013inferring} , we solve this problem by computing the product of the
values of the three-point linkage disequilibrium coefficient with the product of
the allele frequency differences. Using equation \ref{local_ancestry} we obtain $$
\delta_x\delta_y\delta_z
D_3(d,d')=\delta_x^2\delta_y^2\delta_z^2\mathbb{E}[\text{cov}(A_x,A_y,A_z)], $$
because the local ancestry in the admixed sample is independent of the allele
frequencies in the admixed population. For inference purposes, we estimate this
function by averaging over triples of SNPs which are separated by distances of
approximately $d$ and $d'$. The LD term is estimated from the admixed
population, while the $\delta$'s are estimated from reference populations which
are closely related to the two source populations. We notice that both this
approach, as well as the previous approaches (e.g., \cite{loh2013inferring} ),
does not take genetic drift in the source populations after the time of
admixture into account, i.e. there is an assumption of both this method and
previous methods that the allele frequencies in the ancestral source populations
can be approximated well using the allele frequencies in the extant populations.

@@

The time complexities for the binning and the FFT's are $O(S_n)$ and
$O(P^2\log(P))$. Of these two, the first term will dominate, because $P$, the
number of bins, much less than $S_n$, the number of segregating sites.

When only one source population is available,
